Analysis_dec2019

### 2019-12-12 analysis/analysis_dec2019.Rmd
update two main analysis scripts
update main analysis script

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(egg)
theme_set(theme_few())
```

## Read in list of detections (takes forever)
```{r cars}
data_file = "../data/all_frames.csv"
detections =read.csv(data_file)
```

### Filter flipped videos
```{r}
right_side_up_file = "video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

@@

d <- detections %>%
  filter(!vid_name %in% flipped_videos$video)
```

## Read in turk annotations
```{r}
## Need to be able to merge turk annotations with openpose detections but don't understand how vid_name and frame number map onto .jpg names in the image names -- assuming sample index is first b/c max val ~24K

turk_annotations = "../data/turk_annotations_dec5.csv" # first 20 turkers
gold_set = read.csv(turk_annotations)

## cleanup goldset annotations so we can merge
g <- gold_set %>%
  filter(is.na(sanity_check_category)) %>% # don't consider sanity check images here
  filter(!is.na(hands)) %>%
  filter(!is.na(faces)) %>%
  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
  filter(!is.na(sample_ind))  %>%
  mutate(vid_name = str_split(vid_name_temp,".mp4")[[1]][1]) %>%
  filter(!vid_name %in% flipped_videos$video)

## standardize for merging with detectinos
g$vid_name = as.factor(g$vid_name)
g$frame = g$frame_ind

# what <- gold_set %>%
#   filter(is.na(sample_ind))
```

```{r}
# no_openpose <- merged %>%
#   filter(is.na(face_openpose))
# 
# ## never run on openpose?
# unique(no_openpose$vid_name)
# "A_20150507_3124_01"

@@

```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

m <- merged %>%
  select(vid_name, frame, response, hands, faces, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path ) %>%
  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
  rowwise() %>%
  mutate(face_eval = evaluate_detector(faces, face_openpose), hand_eval = evaluate_detector(hands, hand_openpose))
```

### Now calculate prfs - these are SUPER bad and not sure what is up.
```{r}
 return_prf = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
}

return_prf(m$face_eval)
return_prf(m$hand_eval)

@@

# Examine age-trends in open-pose detections
### Make age bins
```{r}
### What ages do we have detections at?

hist(d$age_days)
## bin age by 10 days
bin_size = 30
min_age = min(d$age_days)
max_age = max(d$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

@@

```{r}
summary_by_age <- d %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)

# for geom_smooth
summary_by_age$age_day_bin=as.numeric(summary_by_age$age_day_bin)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(egg)
theme_set(theme_few())
```

## Read in list of detections (takes forever)
```{r cars}
data_file = "../data/all_frames.csv"
detections=read.csv(data_file) 
```

### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
```{r}
right_side_up_file = "../data/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

@@

# d <- detections %>%
#   filter(!vid_name %in% flipped_videos$video)
```

### Read in turk annotations (hand/face present only here, ~4K images)
```{r}
turk_annotations = "../data/turk_annotations_dec5.csv" # 20 turkers who did ~250 frames each
gold_set = read.csv(turk_annotations)

## cleanup these goldset annotations so we can merge
g <- gold_set %>%
  filter(is.na(sanity_check_category)) %>% # don't consider sanity check images here
  filter(!is.na(hands)) %>%
  filter(!is.na(faces)) %>%
  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
  filter(!is.na(sample_ind))  %>% 
  rowwise() %>%
  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1]) %>% ## includes .avi as does detections structure
  filter(!vid_name_short %in% flipped_videos$video)

# length(unique(g$vid_name))

## standardize for merging with detectinos
# g$vid_name = as.factor(g$vid_name)
g$frame = g$frame_ind

# double_check <- gold_set %>%
#   filter(is.na(sample_ind)) -- there's a video that doesn't have detections that is in the gold set
```

### Merge gold set turk annotations and openpose detections
```{r}
# no_openpose <- merged %>%
#   filter(is.na(face_openpose))
# 
# ## never run on openpose?
# unique(no_openpose$vid_name)
# "A_20150507_3124_01"

@@

### Can also import segmentations (this is only a small sample of 200 frames right now)
```{r}
turk_annotations_seg = "../data/turk_segmentations_dec12.csv" # 20 turkers who did ~250 frames each
gold_set_seg = read.csv(turk_annotations_seg)
g_seg <- gold_set_seg %>%
  mutate(hands_seg = (label %in% c("Child hand","Adult hand")), face_seg = (label == "Face")) %>%
  mutate(short_image_path = str_split_fixed(full_image_path,'/',7)[,7]) %>%
  mutate(sample_ind = str_split_fixed(short_image_path,"-",3)[,1], frame_ind_temp = str_split_fixed(short_image_path,"-",3)[,3], vid_name_temp = str_split_fixed(short_image_path,"-",3)[,2]) %>%
  mutate(sample_ind = as.numeric(sample_ind), frame_ind = as.numeric(str_split_fixed(frame_ind_temp,".jpg",3)[,1])) %>%
  rowwise() %>%
  mutate(vid_name_short = str_split(vid_name_temp,"[.]")[[1]][1]) %>%
  mutate(vid_name = str_split_fixed(vid_name_temp,".mp4",2)[,1])

## And merge with detections
merged_g_seg <- g_seg %>%
  mutate(frame = frame_ind) %>%
  left_join(detections)
```

### Write functions to compute TP/FN/TN/FP
```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

## Compute TP/FN/TN/FP on dataset for both faces and hands
```{r}
m <- merged %>%
  select(vid_name, frame, response, hands, faces, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path, age_days, child_id) %>%
  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
  rowwise() %>%
  mutate(face_eval = evaluate_detector(faces, face_openpose), hand_eval = evaluate_detector(hands, hand_openpose))

### on segmentation turk hits as well...
m_seg <- merged_g_seg %>%
  select(vid_name, frame, label, hands_seg, face_seg, sample_ind, face_openpose, hand_openpose, short_image_path, full_image_path, age_days, child_id) %>%
  mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
  rowwise() %>%
  mutate(face_eval = evaluate_detector(face_seg, face_openpose), hand_eval = evaluate_detector(hands_seg, hand_openpose))

### Write functions for returning prfs/f-scores
```{r}
 return_prf_short = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
 }

 return_fscore = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(f)
}
```

### Load ketan's annotation and get prfs
```{r}
load('preprocessed_data/ketan_gold_sample.RData')
# 
 ketan_gold_out <- ketan_gold %>%
   rowwise() %>%
   mutate(vid_name = str_split_fixed(vid_name,".mp4",2)[,1])%>%
   mutate(vid_name_short = str_split(vid_name,"[.]")[[1]][1]) %>%
   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
   rename(face_present_ketan = face_present, hand_present_ketan = hand_present)

 out <- ketan_gold_out %>%
   mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))

return_prf_short(out$face_eval_ketan)
return_prf_short(out$hand_eval_ketan)
```

### How do these f-scores change when we get rid of the weird videos?
```{r}
out_no_flipped <- ketan_gold_out %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))  %>%
  filter(!vid_name_short %in% flipped_videos$video)

return_prf_short(out_no_flipped$face_eval_ketan)
return_prf_short(out_no_flipped$hand_eval_ketan)

### How much do Ketan and turkers agree? 
```{r}
ketan_vs_turk <- ketan_gold_out %>%
  left_join(m) %>%
  mutate(turk_vs_ketan_face = (face_present_ketan == faces))

##
agreement = mean(ketan_vs_turk$turk_vs_ketan_face, na.rm=TRUE)
num_examples = sum(!is.na(ketan_vs_turk$turk_vs_ketan_face))

```
Ketan & turkers agreed `r agreement` percent of the time for the `r num_examples` we tested.

### Merge age/child information from other dataframe back into ketan's gold set by frame/vid_name
```{r}
vid_info <- detections %>%
  select(vid_name, frame, age_days, child_id)

d <- ketan_gold_out %>%
  left_join(vid_info, by=c("vid_name","frame"))
```

### What ages do we have detections at?
```{r}
# hist(d$age_days)
## bin age by 10 days
bin_size = 10
min_age = min(d$age_days)
max_age = max(d$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
d <- d %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))

### Write function to return prfs and num samples so we can look at changes by age/child
```{r}
 return_prf = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  num_detect = length(eval)
  out <- data.frame(p,r,f,num_detect)
  return(out)
 }

prf_by_age <- d %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose)) %>%
  group_by(age_day_bin, child_id) %>%
  do(return_prf(.$face_eval_ketan))
```

```{r}
face_vs_hands_goldset <- d %>%
  group_by(child_id, age_day_bin) %>%
  summarize(prop_faces = sum(face_present_ketan) / length(face_present_ketan), prop_hands = sum(hand_present_ketan) / length(hand_present_ketan), num_detect = length(face_present_ketan)) %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

face_vs_hands_goldset$age_day_bin  = as.numeric(face_vs_hands_goldset$age_day_bin)

ggplot(face_vs_hands_goldset, aes(x=age_day_bin, y=faces_vs_hands, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth()

```{r}
prf_by_age$age_day_bin = as.numeric(prf_by_age$age_day_bin)

p1  = ggplot(prf_by_age, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth()

p2 = ggplot(prf_by_age, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth()

p3 =ggplot(prf_by_age, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth()
#
ggarrange(p1,p2,p3)

```{r}
return_prf(m$face_eval)
return_prf(m$hand_eval)

f_scores_by_age_faces <- m %>%
  group_by(age_days, child_id) %>%
  summarize(f_score_faces = return_fscore(face_eval), num_detect = length(face_eval))

ggplot(f_scores_by_age_faces, aes(x=age_days, y=f_score_faces, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth()
```

```{r}
f_scores_by_age_hands <- m %>%
  group_by(age_days, child_id) %>%
  summarize(f_score_hands = return_fscore(hand_eval), num_detect = length(hand_eval))

ggplot(f_scores_by_age_hands, aes(x=age_days, y=f_score_hands, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth()

@@

# Examine age-trends in open-pose detections
### Make age bins

@@

```{r}
summary_by_age <- detections %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/bin_size,1))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect)

# for geom_smooth
summary_by_age$age_day_bin=as.numeric(summary_by_age$age_day_bin)
